---
title: 'Statistics : Homework No. 07'
author: "Levon Khachatryan"
date: 'Due time/date: 21:20, 4 December, 2018'
output: html_document
---
R version is following:
```{r}
R.version.string
```
I converted xlsx to csv, due to the import of the xlsx file I had some problems with read.xlsx package, but i think it doesn't matter.
```{r echo=FALSE}
```
## Problem 4.
At first let's import necessary file:
```{r}
rm(list = ls())
setwd("D:/MyProjects/StatisticHomeworks/Homework7")
dat <- read.csv("Hw07p04.csv", stringsAsFactors = FALSE,header = FALSE)
head(dat)
```
**$\hat{p}$** has the following form:<br /><br />
$\hat{p} = \frac{X_{1}+X_{2}+...+X_{10}}{10}$<br /><br />
For future calculations, I will add a new column **p** to our data set, where the appropriate value for $\hat{p}$ will be stored.
```{r}
dat["p"] <- rowSums( dat[,2:11] )/10
head(dat)
```
1) Construct the distribution (histogram and KDE) of $\hat{p}$
```{r}
set.seed(1)
p.hat <- dat[,"p"]
hist(p.hat, freq = FALSE)
dens <- density(p.hat)
lines(dens)
```
```{r echo=FALSE}
```
2) calculate the mean of all estimates $\hat{p}$
```{r}
mean(p.hat)
```
3) What do you think, was the coin fair ?<br /><br />
I think that 150 experiments are not enough to say something about the fairness of the coin , but if I supposed to say something, I will say that it is not a fair coin, because the mean is not equal to 5.
```{r echo=FALSE}
```
## Problem 5 - d
So my estimator is the following:<br /><br />
$\hat{\lambda}_{n}=\frac{X_{1}+X_{2}+...+X_{n}}{n+1}$
```{r}
rm(list = ls())
setwd("D:/MyProjects/StatisticHomeworks/Homework7")
dat1 <- read.csv("Hw07p05.csv", stringsAsFactors = FALSE,header = FALSE)
head(dat1)
```
My task is to construct the histogram and KDE for the estimator $\hat{\lambda}_{10}$.
```{r}
dat1["l"] <- rowSums(dat1[,1:10])/11
head(dat1)
```
I will do the same as in the 4th example.
```{r}
set.seed(1)
l.hat <- dat1[,"l"]
hist(l.hat, freq = FALSE)
dens <- density(l.hat)
lines(dens)
```
```{r echo=FALSE}
```
## Problem 6 - b
```{r}
NumberOfTrials <- 200
ListOfMax <- list()
ListOfMin <- list()
for (i in 1:NumberOfTrials){
  SeqFromUnif <- runif(n = 100, min = -1, max = 1)
  ListOfMax[[i]] <- max(SeqFromUnif)
  ListOfMin[[i]] <- min(SeqFromUnif)
  TheoriticalPDF <- dunif(SeqFromUnif)
}
ListOfMax <- as.numeric(ListOfMax)
ListOfMin <- as.numeric(ListOfMin)
```
For $X_{(n)}$ it will be the following:
```{r}
set.seed(1)
hist(ListOfMax, freq = FALSE)
dens <- density(ListOfMax)
lines(dens)
```
```{r echo=FALSE}
```
And for $X_{(1)}$:
```{r}
set.seed(1)
hist(ListOfMin, freq = FALSE)
dens <- density(ListOfMin)
lines(dens)
```
```{r echo=FALSE}
```
The theoretical PDF obtained from the above calculations is follows:
```{r}
plot(TheoriticalPDF)
```
